PIK3CA mutation prediction

### 2020-03-24 pancancer.Rmd
bibliography

---
title: "PIK3CA mutation prediction"
output: "html_document"
---

@@

Breast cancer with PIK3CA mutation has been approved to use PIK3CA inhibitor in hormone receptor positive HER2 negative subtype. Prediction of PIK3CA mutation was done by gene expression data of TCGA.

>>>>

---
title: "PIK3CA mutation prediction"
output: "html_document"
bibliography: bibliography.bib
---

@@

- PIK3CA mutation in selecting drug

Breast cancer with PIK3CA mutation has been approved to use PIK3CA inhibitor in hormone receptor positive HER2 negative subtype. Prediction of PIK3CA mutation was done by gene expression data of TCGA.[]

- Predicting mutation by gene expression data
  * What for?  
  * Feasible?  
  * Cost?

- Varing frquency of PIK3CA mutation across cancer types  
  * High in endometrial breast  
  * not common other cancer type

Universial prediction using gene expression data across cancer type for certain kind of mutation. It's clinically useless now, but we want to explore the possibilities of the PIK3CA mutation prediction.
